GNSS-based displacement detection using Bayesian inference

### 2020-11-16 paper/manuscript.tex
add bd9_3_up.opju
add intro

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Journal of Geodesy}
%
\begin{document}
\linenumbers
\title{GNSS displacement detection based on Bayesian inference
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}

@@

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
%GNSS在位移探测中扮演的角色，以及位移探测的要求
%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\citep{teunissen2017springer}. 
Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\citep{awange2012environmental}, industrial measurement\citep{pavasovic2011application}, and other fields. 
Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\citep{shen2019a}. 
Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
Previous studies on displacement detection based on GNSS pay more attention to how to improve the positioning accuracy. The research on how to identify and extract displacement from the coordinate sequence obtained by GNSS is limited.
%位移探测算法回顾，传统位移探测的弊端
%位移探测的短板

%本文拟采取的措施弥补这些短板
%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情

@@

>>>>

%
% \usepackage{mathptmx}      % use Times fonts if available on your TeX system
%
% insert here the call for the packages your document requires
%\usepackage{latexsym}
% etc.
%
% please place your own definitions here and don't use \def but
% \newcommand{}{}
%
% Insert the name of "your journal" with
\journalname{Journal of Geodesy}
%
\begin{document}
\linenumbers
\title{GNSS-based displacement detection using Bayesian inference
%\thanks{Grants or other notes
%about the article that should go on the front page should be
%placed here. General acknowledgments should be placed at the end of the article.}
}

@@

\section{Introduction}
\label{intro}
%全球定位系统系统的应用-》位移探测
%在自然灾害监测，或者工业测量等领域，GNSS被用于位移探测。
%传统测量仪器的弊端，GNSS位移探测的优势。
%GNSS在位移探测中扮演的角色，以及位移探测的要求
%目前人们对于基于GNSS位移探测的研究更过的关注与如何提高定位的精度，而忽略了如何从GNSS获取的坐标序列中识别并提取位移。
In recent decades, Global navigation satellite system (GNSS) has been widely used in navigation, surveying, and civil aviation as a positioning method\citep{teunissen2017springer}. 
Besides, as a displacement detection method, GNSS has been applied to natural disaster monitoring\citep{awange2012environmental}, industrial measurement\citep{pavasovic2011application}, and other fields. 
Compared with traditional displacement detection technology, GNSS-based displacement detection has many advantages, such as real-time, high accuracy, and weather independence\citep{shen2019a}. 
Displacement detection involves automatic identification of the time of displacement and determination of displacement. 
GNSS-based displacement detection is generally performed by the time-domain difference of GNSS positioning results. 
Previous studies on displacement detection based on GNSS pay more attention to how to improve the positioning accuracy. The research on how to identify and extract displacement from the coordinate sequence obtained by GNSS is limited.

%位移探测算法回顾，
%传统位移探测的弊端
%位移探测的短板
%随着在线监测系统的普及，急需对于单历元动态监测数据进行分析处理，今早发现识别和确定位移。
In \cite{GUMUS2019131}, a displacement monitoring system was designed to evaluate Network Real Time Kinematic(NRTK) for displacement detection. The results showed that NRTK can achieve an accuracy of 4.7 mm and 7.9 mm in the horizontal and vertical directions respectively.

A prototype of a low-cost GNSS has been developed for deep-seated landslide monitoring\citep{rs12203375}. The results of a nine-month filed monitoring period provided a detailed insight into the spatial and temporal pattern of deep-seated landslide surface movements, in which the displacement is obtained by the direct difference between the coordinates of the start and end periods.

In addition, GNSS is also combined with synthetic aperture radar technology for displacement detection, in which long-term GNSS measurements are used as references\citep{atanasova2018ground,fuhrmann2015estimation}.

%本文拟采取的措施弥补这些短板
%目前研究都是基于长周期时间序列进行分析，对于动态定位结果分析的研究还是有限。
%Bayes的优势，并且调研一下前人是否尝试同样的方法干过这类事情

@@

\begin{table*}[h!t]
	\centering
	%	\fontsize{6.5}{8}\selectfont
	\begin{threeparttable}
		\caption{Measured height before and after each movement of the object hanging on the plank, unit (mm).}
		\label{tab_measured_height}
		\begin{tabular}{ccccccccc}
			\toprule
			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
			\midrule
			\multirow{3}*{Step 1} 
			& & ${h_0}$    &371.0&370.9&370.9&371.1&370.9&370.96\\
			& & ${h_1}$    &341.0&341.1&341.5&341.9&341.0&341.30\\
			& & $\Delta h$ & 30.0& 29.8& 29.4& 29.2& 29.9&29.66\\
			\hline
			\multirow{3}*{Step 2} 
			& & ${h_0}$    &340.5&340.1&340.0&340.0&340.1&340.14\\
			& & ${h_1}$    &313.0&312.9&312.9&313.0&313.0&312.96\\
			& & $\Delta h$ &27.5& 27.2& 27.1& 27.0& 27.1& 27.18\\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table*}

\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_bd9_3_up_ts}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_3_up_ts}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_bd9_3_up_tau}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_3_up_tau}
\end{figure}

\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_bd9_3_up_sigma}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_3_up_sigma}
\end{figure} 
\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_bd9_3_up_mu}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_3_up_mu}
\end{figure}

\begin{table*}[h!t]
	\centering
	%	\fontsize{6.5}{8}\selectfont
	\begin{threeparttable}
		\caption{Measured height before and after each movement of the object hanging on the plank, unit (m).}
		\label{tab_measured_height}
		\begin{tabular}{ccccccccc}
			\toprule
			&&&\textbf{1}&\textbf{2}&\textbf{3}&\textbf{4}&\textbf{5}&\textbf{mean}\cr
			\midrule
			\multirow{3}*{Step 1} 
			& & ${h_0}$    &368.5&	368.9&	369.0&	368.9&	369.0&	368.9\\
			& & ${h_1}$    &348.1&	348.0&	348.0&	348.2&	348.3&	348.1\\
			& & $\Delta h$ & 20.4&	 20.9&	 21.0&	 20.7&	 20.7&	 20.7\\
			\hline               
			\multirow{3}*{Step 2}
			& & ${h_0}$    &347.5&	347.3&	347.6&	347.5&	347.4&	347.5\\
			& & ${h_1}$    &326.1&	326.3&	326.1&	326.0&	326.1&	326.1\\
			& & $\Delta h$ & 21.4&	 21.0&	 21.5&	 21.5&	 21.3&	 21.3\\
			\hline               
			\multirow{3}*{Step 3}
			& & ${h_0}$    &325.0&	325.1&	324.9&	325.0&	325.2&	325.0\\
			& & ${h_1}$    &305.5&	305.3&	305.4&	305.5&	305.6&	305.5\\
			& & $\Delta h$ & 19.5&	 19.8&	 19.5&	 19.5&	 19.6&	 19.6\\
			\bottomrule
		\end{tabular}
	\end{threeparttable}
\end{table*}
\begin{figure}[H]
	\centering
	\includegraphics[width=10 cm]{v_bd9_4_up_ts}
	\caption{Daily displacement of experimental data obtained by the ionosphere-free PPP static model.}
	\label{fig_v_bd9_4_up_ts}
\end{figure}
